\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2013-04-08 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
updated the users manual regarding CPML

\begin{description}
\item [absorbing\_cpml\_file] {\bf (only in case of C-PML absorbing conditions)} Contains at the first line respectively the "number of C-PML spectral elements"
and the "thickness of C-PML layers" (currently, a common thickness for all faces is defined but this can be easily adapted in the future if needed by the setting of CPML\_width\_x, CPML\_width\_y, CPML\_width\_z parameters). On all following lines are defined the "C-PML spectral elements global indexing" and "C-PML regions" for each
C-PML element according to the following convention:

\begin{itemize}
\item \#id\_cpml\_regions = 1 : X\_surface C-PML,
\item \#id\_cpml\_regions = 2 : Y\_surface C-PML,
\item \#id\_cpml\_regions = 3 : Z\_surface C-PML,
\item \#id\_cpml\_regions = 4 : XY\_edge C-PML,
\item \#id\_cpml\_regions = 5 : XZ\_edge C-PML,
\item \#id\_cpml\_regions = 6 : YZ\_edge C-PML,
\item \#id\_cpml\_regions = 7 : XYZ\_corner C-PML.
\end{itemize}

>>>>

\begin{description}
\item [absorbing\_cpml\_file] {\bf (only needed in case of C-PML absorbing conditions)}
Contains on the first line the total number of C-PML spectral elements in the mesh,
and then on the following line the list of all these C-PML elements with two numbers per line:
first the spectral element number, and then a C-PML flag indicating to which C-PML layer(s)
that element belongs, according to the following convention:

\begin{itemize}
\item Flag = 1 : element belongs to a X CPML layer only (either in Xmin or in Xmax),
\item Flag = 2 : element belongs to a Y CPML layer only (either in Ymin or in Ymax),
\item Flag = 3 : element belongs to a Z CPML layer only (either in Zmin or in Zmax),
\item Flag = 4 : element belongs to a X CPML layer and also to a Y CPML layer,
\item Flag = 5 : element belongs to a X CPML layer and also to a Z CPML layer,
\item Flag = 6 : element belongs to a Y CPML layer and also to a Z CPML layer,
\item Flag = 7 : element belongs to a X, to a Y and to a Z CPML layer, i.e., it belongs to a CPML corner.
\end{itemize}

Note that it does not matter whether an element belongs to a Xmin or to a Xmax CPML, the flag
is the same in both cases; the same is true for Ymin and Ymax, and also Zmin and Zmax.

When you have an existing CUBIT (or similar) mesh stored in SPECFEM3D format,
i.e., if you have existing "nodes\_coords\_file" and "mesh\_file" files but do not know how to assign
CPML flags to them, we have created a small serial Fortran program that will do that automatically
for you, i.e., which will create the "absorbing\_cpml\_file" for you.
That program is
utils/CPML/convert\_external\_layers\_of\_a\_given\_mesh\_to\_CPML\_layers.f90, and a small Makefile
is provided in that directory (utils/CPML).

IMPORTANT: it is your responsibility to make sure that in the input CUBIT (or similar) mesh
that this code will read in SPECFEM3D format from files "nodes\_coords\_file" and "mesh\_file"
you have created layers of elements that constitute a layer of constant thickness aligned
with the coordinate grid axes (X, Y and/or Z), so that this code can assign CPML flags to them.
This code does NOT check that (because it cannot, in any easy way).
The mesh inside these CPML layers does not need to be structured nor regular, any non-structured
mesh is fine as long as it has flat PML inner and outer faces, parallel to the axes, and thus
of a constant thickness.
The thickness can be different between the X, Y and Z sides. But for X it must not vary,
for Y it must not vary, and for Z it must not vary.
If you do not know the exact thickness, or if you think the thickness may have tiny variations,
for instance due to roundoff issues when exporting the mesh, you can use a slightly LARGER value
in this code (say 2\% to 5\% more), and this code will fix that and will adjust it; never use
a SMALLER value otherwise this code will miss some CPML elements.

Note: in a future release we will remove the constraint of having CPML layers aligned with the
coordinate axes; we will allow for meshes that are titled by any constant angle in the horizontal plane.
However this is not implemented yet.
